### 2017-02-24 Conclusion/Conclusion.tex
More editing, plus additional cosmetic fixes from quick skim

The search for a heavy Higgs boson decaying to a final state of $bb\Pgt\Pgt$ via two
$125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
centre of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the MSSM phase space not easily accessible via other channels.
To separate more signal-like and more background-like events, a categorisation based on the number of 
b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
mass in a window around $125\,\GeV$ are used in combination with a kinematic fitting technique for
the reconstruction of the 4-body mass.
The resulting mass variable provides good separation between the signal and the dominant
\ttbar background, and is thus used as the variable for signal extraction. 
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range $260<m_H<350\,\GeV$. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-\tanb~MSSM scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario \cite{CMS-HIG-14-034}.

>>>>

The search for a heavy Higgs boson decaying to a final state of $\Pbottom\Pbottom\Pgt\Pgt$ via two
$125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
centre of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the MSSM phase space not easily accessible via other channels.
To separate more signal-like and more background-like events, a categorisation based on the number of 
b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-b
mass in a window around $125\,\GeV$ are used in combination with a kinematic fitting technique for
the reconstruction of the 4-body mass.
The resulting mass variable provides good separation between the signal and the dominant
\ttbar background, and is thus used as the variable for signal extraction. 
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range $260<m_{\PHiggs}<350\,\GeV$. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-\tanb~MSSM scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario \cite{CMS-HIG-14-034}.

### 2017-02-24 Detector/Detector.tex
More editing, plus additional cosmetic fixes from quick skim

The data-taking efficiency of CMS is not 100\%, as parts of the detector might be
switched off while collisions are ongoing. In 2012 the data-taking 
efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.4\%
From all of the data that is recorded only a subset is used for analysis. Data is 
certified as good for use in analyses if it is known that all relevant sub-detectors
were functioning correctly. In 2012 the certification efficiency was 90.4\%, 
meaning all sub-detectors were working well for a dataset corresponding to $19.7\,\invfb$. %MAYBE COME BACK TO LATER?
Due to cryogenic issues the certification efficiency with the magnet operating
at $3.8\,\tesla$ was 60.4\% in 2015, leading to $2.3\,\invfb$ of 
analysable data for which the full detector was operational. An additional $0.6\,\invfb$
was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
the certification efficiency was 95.4\%, resulting in $36.3\,\invfb$ of data marked good %FIXME: certification efficiency
for use in analyses.

>>>>

The data-taking efficiency of CMS is not 100\%, as parts of the detector might be
switched off while collisions are ongoing. In 2012 the data-taking 
efficiency was 93.5\%, in 2015 it was 90.3\% and in 2016 it was 92.0\%
From all of the data that is recorded only a subset is used for analysis. Data is 
certified as good for use in analyses if it is known that all relevant sub-detectors
were functioning correctly. In 2012 the certification efficiency was 90.4\%, 
meaning all sub-detectors were working well for a dataset corresponding to $19.7\,\invfb$. %MAYBE COME BACK TO LATER?
Due to cryogenic issues the certification efficiency with the magnet operating
at $3.8\,\tesla$ was 60.4\% in 2015, leading to $2.3\,\invfb$ of 
analysable data for which the full detector was operational. An additional $0.6\,\invfb$
was taken with the \ac{CMS} magnet switched off. For the full 2016 p-p running period
the certification efficiency was 95.0\%, resulting in $35.9\,\invfb$ of data marked good %FIXME: certification efficiency
for use in analyses.

### 2017-02-24 Hhh/Hhh.tex
More editing, plus additional cosmetic fixes from quick skim

If there is more than one possible \etau pair, the pair with the largest \pT$^{\Pe}$+\pT$^{\Pgth}$
is taken. Similar additional vetoes as in the \mutau channel are applied.
The event is rejected if an opposite-charge pair of electrons with \pT~ $> 15\,\GeV$, passing looser ID and
isolation requirements than the signal electron requirements, can be formed. To prevent overlap with other channels and to reduce the di-boson
background, events that have more than one electron or at least one muon passing \pT~$>10\,\GeV$ and loose ID and isolation
requirements are rejected.

@@

\section{\acl{MC} simulation to data correction factors}
\label{sec:hhh_datamc}
\ac{MC} samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation to data 
correction factors used for this are estimated in dedicated control regions.

Identification, isolation, and trigger efficiencies are measured for electrons, muons
and hadronic taus in data and simulated events.
The difference between
the efficiencies in data and simulated events are applied to \ac{MC} events as a
scale factor $\text{SF} = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.

@@

The energy scale for hadronic taus is determined by fitting the mass of the 
hadronic tau candidate in $\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.
This fit is performed separately for each hadronic tau decay mode to obtain
an energy scaling that is applied to reconstructed hadronic taus matched
to simulated hadronic tau decays in \ac{MC} events.

@@

Differences in \MET~resolution and response between data and simulation are accounted for by
applying recoil corrections to \Zellell, \Wjets and signal \ac{MC} events. Section \ref{sec:objects_met_recoilcorr} 
gives more details on how these corrections are derived.

To correct for the differences in b-tagging efficiency and light jet mis-tagging
rates between data and simulation, \pT~and $\eta$~dependent scale factors are 
derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
b-/c-jets and light jets. In this analysis the ``promote/demote'' method
is used to apply these.

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - \text{SF} \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
\end{align}
Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b-tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
under consideration.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category the total
yield after the initial event selection, before subdividing into categories, as
estimated in the \Ztautau \ac{MC} sample is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using \ac{MC} samples.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to low-\mT~extrapolation
 factor is determined from the \Wjets \ac{MC} 
sample. The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

@@

The shapes in all categories are taken from same-sign data with the electron or muon
isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
inverting the light lepton isolation requirements, the category definition
is relaxed to obtain the shapes. For the purposes of QCD shape
estimation, jets are considered b-tagged if they pass the loose b-tagging
working point.
\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shapes and normalisations are
estimated using \ac{MC} samples.

@@

The uncertainty on the luminosity measurement amounts to 2.6\% \cite{CMS-PAS-LUM-13-001} for data collected during

@@

A systematic uncertainty on the efficiency measurements
for the leptons is derived by combining the separate uncertainties on these measurements

@@

The uncertainty on both the $\Pe\rightarrow\Pgth$ fake rate measurement and the

@@

Uncertainties on the \MET~resolution and response are estimated by varying

@@

\item \ttbar: The uncertainty on the \ttbar cross section is 10\% \cite{SMHtautauCMS}.
\item Di-boson and single top: The combined uncertainty on the di-boson and single-top cross sections is 15\% \cite{SMHtautauCMS}.
\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty on this yield estimate is primarily due to the number of events available in the control region. The uncertainty ranges from 10\% in the 2jet-0tag category to 100\% in the 2jet-2tag category.

@@

The uncertainties on the jet energy corrections are applied by shifting the jet energy up and down by the \pT-and $\eta$-dependent uncertainty \cite{cms-jec-2011}. Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.

@@

More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.
Systematic uncertainties are also applied in the \AtoZhtolltautau analysis. 
For the purpose of combining the results with the \Htohhtobbtautau search,
some of these are correlated between the two analyses.
This applies to the
luminosity uncertainty and the uncertainties on b-tagging efficiency
and light jet mis-tagging rate.

@@

\subsubsection{Interpretation in a type-II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
As discussed in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
free parameters than a particular \ac{MSSM} benchmark scenario. To leave
just two free parameters, it is enough to fix the masses of the five Higgs bosons
and take the quartic couplings to be zero.
For the interpretation shown here the assumption that \mA=\mH=\mHplus~$=300\,\GeV$ is made.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\Htohhtobbtautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/Hhh2HDM.pdf}}
\subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZh2HDM.pdf}}
\caption[Search for \Htohhtobbtautau and search for \AtoZhtolltautau
interpreted in a type-II 2HDM, assuming \mA=\mH=\mHplus~$=300\,\GeV$.]{Search for (a) \Htohhtobbtautau and (b) \AtoZhtolltautau interpreted in a type-II 
\ac{2HDM}, assuming \mA=\mH=\mHplus~$= 300\,\GeV$. The expected (dashed line)
and observed (solid line) exclusion contours at 95\% \ac{CL} are overlaid
on the \xsbr of the searched-for process.
Regions of the \cosba-\tanb~plane where the 
\xsbr is larger than the model-independent upper limit set for $m_{\PHiggs} = 300\,\GeV$ 
(see figures \ref{fig:AZhUpperLimits} and \ref{fig:hhh_results_modelindep}) are excluded.}
\label{fig:HhhandAZh2HDMOverlaid}
\end{center}
\end{figure}

>>>>

If there is more than one possible \etau pair, the pair with the largest \pT$^{\Pe}$+\pT$^{\Pgth}$
is taken. Similar additional vetoes as in the \mutau channel are applied.
The event is rejected if an opposite-charge pair of electrons with $\pTm > 15\,\GeV$, passing looser ID and
isolation requirements than the signal electron requirements, can be formed. To prevent overlap with other channels and to reduce the di-boson
background, events that have more than one electron or at least one muon passing \pT~$>10\,\GeV$ and loose ID and isolation
requirements are rejected.

@@

\section{\acl{MC} simulation to data correction factors}
\label{sec:hhh_datamc}
Simulated samples are used for the estimation of some of the backgrounds and the signal, 
and it is therefore important to correct for any mis-modelling. The \ac{MC} simulation to data 
correction factors used for this are estimated in dedicated control regions.

Identification, isolation, and trigger efficiencies are measured for electrons, muons
and hadronic taus in data and simulated events.
The difference between
the efficiencies in data and simulated events are applied to simulated events as a
scale factor $\text{SF} = \frac{\epsilon_{\text{Data}}}{\epsilon_{\text{MC}}}$.

@@

The energy scale for hadronic taus is determined by fitting the mass of the 
hadronic tau candidate in $\PZ\rightarrow\Pgt\Pgt\rightarrow\Pgm\Pgth$ events.
This fit is performed separately for each hadronic tau decay mode to obtain
an energy scaling that is applied to reconstructed hadronic taus matched
to simulated hadronic tau decays in simulation.

@@

Differences in \MET~resolution and response between data and simulation are accounted for by
applying recoil corrections to \Zellell, \Wjets and signal simulation. Section \ref{sec:objects_met_recoilcorr} 
gives more details on how these corrections are derived.

To correct for the differences in b-tagging efficiency and light jet mis-tagging
rates between data and simulation, \pT~and $\eta$~dependent scale factors are 
derived using the method described in reference \cite{BTV8TeV}. There are separate scale factors for 
b-/c-jets and light jets. In this analysis the ``promote-demote'' method
is used to apply these.

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - \text{SF} \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(\text{SF} - 1)(\epsilon_{\text{MC}}-1)}{\text{SF}} \text{    for SF > 1},
\end{align}
Where SF is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b-tagging efficiency in simulated events for the type of jet (light, b- or c-)
under consideration.

@@

\section{Background estimation}
\label{sec:hhh_backgrounds}
To estimate the shape and yield of backgrounds in this analysis, data-driven techniques are
used where possible. 
\subsection{\texorpdfstring{\Ztautau}{Z to tau tau}}
\label{sec:hhh_backgrounds_ztt}
The \Ztautau background is estimated using the embedded samples
described in section \ref{sec:hhh_datasets}. To estimate the 
yield of \Ztautau in each category the total
yield after the initial event selection, before subdividing into categories, as
estimated in the simulated \Ztautau sample is scaled by the efficiency with which 
such events pass the category selection in the embedded sample. The shape of
the \Ztautau background is taken from the embedded sample after applying the full
category selection. The contamination from the \ttbar background in the embedded
sample is evaluated using the dedicated \ttbar embedded sample. This contribution
is subtracted from the \Ztautau background.
\subsection{\texorpdfstring{\ttbar}{ttbar}}
Both the \ttbar shape and normalisation are estimated using simulation.
These are checked against data in dedicated control regions. One such control
region uses the \emu final state of the di-tau pair. A correction factor is estimated in 
this control region and applied to the yield estimate from simulation in the signal region. 
%The resulting scale factor is 1.033 ± 0.013(stat.) ± 0.088(syst.). 
\subsection{\texorpdfstring{\Wjets}{W + jets}}
\label{sec:hhh_backgrounds_wjets}
The \Wjets background is greatly reduced by requiring \mT~to
be less than $30\,\GeV$. To estimate the remaining contribution
in the signal region a sideband with \mT~greater
than $70\,\GeV$ is used in the 2jet-0tag and 2jet-1tag categories.
Contributions from other backgrounds are subtracted 
from the data in this region, and a high-\mT~to low-\mT~extrapolation
 factor is determined from the \Wjets simulation.
The yield in the signal region is given by the data yield in the high-\mT~sideband, with
other backgrounds subtracted, multiplied by this extrapolation factor.
In the 2jet-2tag category, a slightly different high-\mT~sideband of $60$--$120\,\GeV$ is used 
as above $120\,\GeV$ the \ttbar background dominates over \Wjets. 
The method of extrapolating this yield estimate into
the signal region is otherwise analogous.

@@

The shapes in all categories are taken from same-sign data with the electron or muon
isolation inverted. For the 2jet-1tag and 2jet-2tag categories, in addition to 
inverting the light lepton isolation requirements, the category definition
is relaxed to obtain the shapes. For the purposes of QCD shape
estimation, jets are considered b-tagged if they pass the loose b-tagging
working point.
\subsection{Other backgrounds}
\label{sec:hhh_backgrounds_other}
The remaining backgrounds of \Zellell, di-boson and single-top
events are small. Both shapes and normalisations are
estimated using simulated samples.

@@

The uncertainty in the luminosity measurement amounts to 2.6\% \cite{CMS-PAS-LUM-13-001} for data collected during

@@

A systematic uncertainty in the efficiency measurements
for the leptons is derived by combining the separate uncertainties in these measurements

@@

The uncertainty in both the $\Pe\rightarrow\Pgth$ fake rate measurement and the

@@

Uncertainties in the \MET~resolution and response are estimated by varying

@@

\item \ttbar: The uncertainty in the \ttbar cross section is 10\% \cite{toppp}.
\item Di-boson and single top: The combined uncertainty in the di-boson and single-top cross sections is 15\% \cite{8TeVdib,8TeVst}.
\item \Wjets: As the \Wjets yield is estimated from a high \mT~sideband in data, the uncertainty in this yield estimate is primarily due to the number of events available in the control region. The uncertainty ranges from 10\% in the 2jet-0tag category to 100\% in the 2jet-2tag category.

@@

The uncertainty in the jet energy corrections are applied by shifting the jet energy up and down by the \pT-and $\eta$-dependent uncertainty \cite{cms-jec-2011}. Again, as this affects the shape of the kinematic fit mass distribution this uncertainty is applied as a shape uncertainty.

@@

More detail on this analysis can be found in reference \cite{CMS-HIG-14-034}.
Systematic uncertainties are also applied in the \AtoZhtolltautau analysis. 
For the purpose of combining the results with the \Htohhtobbtautau search,
some of these are correlated between the two analyses.
This applies to the
luminosity uncertainty and the uncertainties in the b-tagging efficiency
and the light jet mis-tagging rate.

@@

\subsubsection{Interpretation in a type-II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
As discussed in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
free parameters than a particular \ac{MSSM} benchmark scenario. To leave
just two free parameters, it is enough to fix the masses of the five Higgs bosons
and take the quartic couplings to be zero.
For the interpretation shown here the assumption that $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$ is made.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[\Htohhtobbtautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/Hhh2HDM.pdf}}
\subfloat[\AtoZhtolltautau]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/AZh2HDM.pdf}}
\caption[Search for \Htohhtobbtautau and search for \AtoZhtolltautau
interpreted in a type-II 2HDM, assuming $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$.]{Search for (a) \Htohhtobbtautau and (b) \AtoZhtolltautau interpreted in a type-II 
\ac{2HDM}, assuming $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$. 
The expected (dashed line)
and observed (solid line) exclusion contours at 95\% \ac{CL} are overlaid
on the \xsbr of the searched-for process.
Regions of the \cosba-\tanb~plane where the 
\xsbr is larger than the model-independent upper limit set for $m_{\PHiggs} = 300\,\GeV$ 
(see figures \ref{fig:AZhUpperLimits} and \ref{fig:hhh_results_modelindep}) are excluded.}
\label{fig:HhhandAZh2HDMOverlaid}
\end{center}
\end{figure}
